Supplement History of Cheminformatics as part of Cheminformatics: The Computer Science of Chemical Discovery

### 2011-11-09 supplement_history.tex
Added document for rebuttal. Updated some refs and added them to the suppl history document

  from the lead stage ot the clinical trial stage. Naturally,

@@

  broadly such as in drug repurposing efforts.

@@

\cite{Gasteiger2003} in 2003.  More concise introductory texts

@@

\section{Historical Milestones}
In this section we highlight the development of a variety of
cheminformatics concepts and techniques over time. The first chemical
graphs were drawn by the Scottish chemist Willam Cullen in 1758
\cite{bonchevrouvrey1991}, who initially called them affinity graphs.
After developing the concept of bonds between atoms (Couper, 1858) the
first chemical graphs occured in publications of Brown in 1864 and
Cayley in 1874 \cite{bonchevrouvrey1991,brown2009}.

The year 1946 may be regarded as the birth year of chemoinformatics
\cite{Chen2006}: \textit{``In 1946 King et al.\cite{kct1946} published
  an article illustrating the use of IBM's business accounting
  machines in carrying out the construction of the rotational spectra
  of asymmetric rotors by the evaluation of mathematical equations for
  line position and line intensity''}. One could argue that this is
more of a computational chemistry application. The shorter term
'chemoinformatics' was coined by Brown in 1998\cite{brown1998}, while
the \textit{Journal of Chemical Documentation} (founded in 1961)
changed its name in 1975 to \textit{Journal of Chemical Information
  and Computer Sciences} to reflect the tight connection between
chemical information and computer science. The Chemical Abstract
Service (CAS) of the American Chemical Society (ACS) formed a research
department in 1955 and starting from 1965 they provided their Chemical
Registry System, and in 1968 they made the first computer-readable
file of all abstracted documents available \cite{Chen2006}.

>>>>

  from the lead stage to the clinical trial stage. Naturally,

@@

  broadly such as in drug repurposing
  efforts \cite{Dudley:2011fk,Swamidass:2011uq}.

@@

\cite{Gasteiger2003} in 2003.  More concise, introductory texts

@@

\section{Historical Milestones}
In this section we highlight the development of a variety of
cheminformatics concepts and techniques over time. The shorter term
'chemoinformatics' was coined by Brown in
1998\cite{brown1998}. However, the main journal for this field
(\textit{Journal of Chemical Documentation} was founded in
1961. Interestingly, the journal was renamed to \textit{Journal of
  Chemical Information and Computer Sciences} in 1975 to reflect the
tight connection between chemical information and computer
science. The Chemical Abstract Service (CAS) of the American Chemical
Society (ACS) formed a research department in 1955 and starting from
1965 they provided their Chemical Registry System, and in 1968 they
made the first computer-readable file of all abstracted documents
available \cite{Chen2006}.

From a more technical viewpoint, the first chemical graphs were drawn
by the Scottish chemist Willam Cullen in 1758
\cite{bonchevrouvrey1991}, who initially called them affinity graphs.
After developing the concept of bonds between atoms (Couper, 1858) the
first chemical graphs occured in publications of Brown in 1864 and
Cayley in 1874 \cite{bonchevrouvrey1991,brown2009}.

The year 1946 may be regarded as the birth year of chemoinformatics
\cite{Chen2006}: \textit{``In 1946 King et al.\cite{kct1946} published
  an article illustrating the use of IBM's business accounting
  machines in carrying out the construction of the rotational spectra
  of asymmetric rotors by the evaluation of mathematical equations for
  line position and line intensity''}. One could argue that this is
more of a computational chemistry application.
